
\noindent
A lab report describing what has been done in this project work should be handed in after the project work is completed.  For each part of the exercise the report should include:
\begin{itemize}
    \item Printouts of data from relevant experiments (plots).
    \item Relevant model derivations, calculations and parameter values (remember to include units and scaling).
    \item Discussion and analysis of the results.
    \item Simulink diagrams and MATLAB code(that you've made youself! No templates).
    \item Questions introduced with "For the daring" are optional, but answering them correctly shows good understanding and will give bonus points. (These are not necessay to get full score)
\end{itemize}

Evaluations are based on:
\begin{itemize}
    \item documented calculations,
    \item experimental results,  
    \item analysis and discussion of the results,
    \item answers to questions in exercise sheet,
    \item and the quality of the written documentation of the results will be emphasized. 
\end{itemize}


\begin{align*}\hline\hline\end{align*}

\bigskip
\noindent
You should delete this page. It should not be part of your final PDF!\\

\noindent
In the following pages, we have written a skeleton that you should fill in. The italic text is only for extra guidance and should be deleted.


%\noindent
There should not be a need to add any other (sub)sections.\\

%\noindent
Unless you have a very good reason not to, you should write the report in English. If you want a larger example on how to use \LaTeX, have a look at the template that was used in TTK4115 and previously in this course as well:
\url{https://github.com/ntnu-itk/labreport}. 

